\normalfont \normalsize \textsc{UNSW School of Computer Science and Engineering} \\ [24pt] \horrule{1pt} \\[0.5cm] \LARGE Predict Stock Movements Using News \\ \horrule{1pt} \\[0.5cm]

### 2019-10-29 paper.tex
change names etc

% Block below sets up headers and sectioning.
\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancy} % Makes all pages in the document conform to the custom headers and footers
\fancyhead[L]{z5161938 Ian Thorvaldson} %Page header left -- Student number and name
\fancyhead[C] {} %Page header center -- Empty
\fancyhead[R]{PHYS1241 Assignment 4 2017} %Page header right -- Course/year
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{\thepage} % center footer -- page numbering
\fancyfoot[R]{} % Empty right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{12pt} % Customize the height of the header
%\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
%\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
%\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
%\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

@@

\title{	\normalfont \normalsize
\textsc{UNSW School of Physics} \\ [24pt]
\horrule{1pt} \\[0.5cm] % Thin top horizontal rule
\LARGE PHYS1241 Assignment 4 \\ % The assignment title
\horrule{1pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Ian Thorvaldson z5161938} % Your name

>>>>

% Block below sets up headers and sectioning.
\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancy} % Makes all pages in the document conform to the custom headers and footers
\fancyhead[L]{z5173159 Cecilia Xifei Ni} %Page header left -- Student number and name
\fancyhead[C] {} %Page header center -- Empty
\fancyhead[R]{Predict Stock Movements Using News} %Page header right -- Course/year
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{\thepage} % center footer -- page numbering
\fancyfoot[R]{} % Empty right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{12pt} % Customize the height of the header
%\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
%\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
%\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
%\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

@@

\title{	\normalfont \normalsize
\textsc{UNSW School of Computer Science and Engineering} \\ [24pt]
\horrule{1pt} \\[0.5cm] % Thin top horizontal rule
\LARGE Predict Stock Movements Using News \\ % The assignment title
\horrule{1pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Cecilia Xifei Ni z5173159} % Your name
